Regional Inequalities and economic growth; cross section and times series analysis

### 2023-11-20 MSB104_GR_1_Final_Assignment_research_article.qmd
:D

>>>>

**Random-Effects Models**

@lessmann2017 mention the use of a random-effects model to investigate the determinants of
within-country changes in inequality. The random-effects model controls for several country-level fixed factors (national income, number of regions, and area) and fixed effects for various country groups [@lessmann2017]. The advantage of the random-effects model is that the expected value of the country-specific effect is zero, which means that there is no need to apply any arbitrary data imputation procedure for the missing intercepts [@lessmann2017]. However, this approach may come at the cost of founding the predictions on a slightly biased coefficient [@lessmann2017]. The text also notes that
the major coefficient of interest is not sensitive to applying either a fixed-effects model or a random-effects model with additional country and region information [@lessmann2017].
